Sailing the High Seas:\\ A Christian Exploration of Piracy

### 2024-04-18 paper.tex
expand privacy section

\subsection{Privacy}
As a side note, there are instances where pirated software can be more privacy-oriented
than the paid version. Sometimes the pirated version is ``cracked'' to remove certain
digital rights management (DRM) tools that often run background tasks unbeknownst to the
user. These background tasks often leak bits of information about the user in order to
validate that they are legitimate owners of the software. By collecting information about
users, a business invades the privacy of its user base. However, pirated and cracked
software does not have such DRM because it needed to be removed to allow it to be freely
distributed. Thus, when it comes to software that contains aggressive DRM, piracy offers
better security by default. Unfortunately, some pirated software introduces malicious
code, a subject that will be explored in the next section.

>>>>

\subsection{Privacy}
It would be remiss to discuss the tools of piracy without mentioning virtual private
networks (VPNs) and Tor, formerly known as the onion router. Commercially available VPNs
allow internet users to route their traffic through another machine on the internet before
connecting to the final destination host. What this means to the user is that their
traffic appears to be coming from another IP address than the one for their home network.
Since IP addresses are associated with geographical locations, a VPN can also mask a
user's location from bad actors. However, VPNs are not a perfect solution to privacy. The
company hosting the virtual private network is entrusted with all the user's internet
traffic, so the company should not be left susceptible to cybersecurity attacks or
coercion from government entities that might compromise someone's privacy online. In
general, the user should have confidence in the VPN provider that their information will
not be misused.

In the context of piracy, a VPN enables users to bypass firewalls that block access to
certain locations on the internet and they are employed in combination with the BitTorrent
protocol to protect one's identity when they are connecting to seeders or leechers. When
used responsibly, a privacy-conscious VPN provider is quite the boon to internet users in
countries that oppress certain people groups. As long as the VPN itself is not
compromised, a user's true identity can stay hidden. In the case of a missionary in a
hostile environment, a VPN might enable them to bypass the restrictions that prevent them
from accessing certain online editions of the Bible. Ultimately, VPNs have the ability to
be a tool for good in situations where access to information is limited and where one
might be persecuted if their identity were to be discovered on the internet.

In the same vein as a VPN is Tor. Tor is a service that allows users to browse the
internet without anyone but themselves knowing both the source and destination of a
connection. Unlike a VPN, there is no central company that can see who is connecting to
what destination; the only person who knows that is the one using the service. The Tor
Project writes, \textcquote{tor:about}[.]{\textins{t}he goal of onion routing was to have
a way to use the internet with as much privacy as possible, and the idea was to route
traffic through multiple servers and encrypt it each step of the way} Tor not only
provides privacy, it gives users total anonymity. Similar to using a VPN, connecting to
the Tor network before browsing the internet makes it near impossible for observers to see
what sites someone is accessing and for the site to see where the request is coming from.
The potential applications for near-perfect anonymity on the internet are innumerable.
Those living under oppressive governments can bypass censorship to reach the truth and
Christians can anonymously access the Bible online in restrictive countries, just to name
a few.

As a side note, there are instances where pirated software can be more privacy-oriented
than the paid version. Sometimes the pirated version is ``cracked'' to remove certain
digital rights management (DRM) tools that often run background tasks unbeknownst to the
user. These background tasks often leak bits of information about the user in order to
validate that they are legitimate owners of the software. By collecting information about
users, a business invades the privacy of its user base. However, pirated and cracked
software does not have such DRM because it needed to be removed to allow it to be freely
distributed. Thus, when it comes to software that contains aggressive DRM, piracy offers
better security by default. Unfortunately, some pirated software introduces malicious
code, a subject that will be explored in the next section.
